Describing the scale and composition of police demand in Detroit.

### 2021-08-23 paper.Rmd
fonts

---
title: "Describing the scale and composition of police demand in Detroit."
output: pdf_document
header-includes:
  - \usepackage{lscape}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, comment=F, warning=F)
```

@@

\newpage

\begin{landscape}

```{r fig1, fig.align = "center", fig.cap = "Proportional breakdown of deployed time spent on each incident category."}
knitr::include_graphics("visuals/fig1_time_ann.png")
```

\end{landscape}

\newpage

```{r fig2, fig.align = "center", fig.cap = "Mean incident counts by day and week by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig2_time_heat.png")
```

```{r fig3, fig.align = "center", fig.cap = "Spatial patterning of total incident counts by demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig3_maps.png")
```

>>>>

---
title: "Describing the scale and composition of police demand in Detroit."
author: "Samuel Langton (Netherlands Institute for the Study of Crime and Law Enforcement)"
output: pdf_document
header-includes:
  - \usepackage{lscape}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message=F, comment=F, warning=F, fig.pos = 'H')
library(readr)
library(dplyr)
library(kableExtra)
```

## Introduction

@@

\newpage
```{r fig1, fig.align = "center", fig.cap = "Proportional breakdown of deployed time spent on each incident category.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig1_time_port.png")
```
\newpage

```{r table1}
table1_df <- read_csv("results/table1_des_stats.csv")

kable(table1_df, caption = "Frequency and proportional breakdown (counts and time) for each demand type.",
      booktabs = T, longtable = T, linesep = "", format = "latex") %>%
    kable_styling(latex_options = c("striped"),
                  font_size = 10, full_width = F)
```

## Temporal patterning

\newpage
```{r fig2, fig.align = "center", fig.cap = "Mean incident counts by day and week, for each demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig2_time_heat.png")
```
\newpage

## Spatial patterning

\newpage
```{r fig3, fig.align = "center", fig.cap = "Spatial patterning of total incident counts for each demand type.", out.width = "\\textwidth"}
knitr::include_graphics("visuals/fig3_maps.png")
```
\newpage

## Conclusion
